### 2022-10-21 Progress_10.tex
10

% Summary 
  \section*{Progress meeting 8 | 15 September, 2022}

  \section*{1. Progress}
  \begin{itemize}
  \item \textbf{Teleoperation:}

  \item \textbf{Custom end effector:}

  \item \textbf{Impact detection:}

  \item \textbf{Learning from demonstration:}

  \end{itemize}

>>>>

% Summary 
  \section*{Progress meeting 10 | 24 October, 2022}

  \section*{1. Progress}
  \begin{itemize}
  \item \textbf{Teleoperation:} Last time, I mentioned that the velocity reference results in more responsive tracking of the VR device. This was paired with the safety limits of the robot being exceeded in edge cases. It was suggested that I look into the task weights, however in section xxx I show that changing weights is not a solution. Instead of altering weights, I solved the problem by tuning the reference augmentation.

  \item \textbf{Impact detection:} I implemented impact detection using a jump-aware filter, a prediction function, and a bounding function as described by Mark Rijnen. In section xxx, I argue that a small moving window for the filter is better than a large window. As a result, the prediction is equivalent to a linear extrapolation and the jump-aware filter is redundant. This is supported by experimental data.

  Furthermore, impact detection based on the estimated force rate was compared to Mark Rijnen's approach with position measurements. Comparatively, the force rate method has a lower response time as was already suggested by Sven.

  \item \textbf{Learning from demonstration:} An experiment was performed where the robot stamps on the table. This is further explained in section xxx. Impedance control without reference spreading was compared to impedance control with reference spreading in vertical direction. The addition of reference spreading reduced the required control effort and joint torques at the time of impact. The implementation should be expanded to also support reference spreading in rotational DoF's so that more complex tasks than just stamping can be performed. Furthermore, an intermediate impact control mode should be investigated.

  \item \textbf{Use case:} 
  \end{itemize}
